\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.85in]{geometry}
\usepackage{xcolor}                
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}          
\usepackage{parskip}

% Colors
\definecolor{heading}{RGB}{0,70,150}
\definecolor{accent}{RGB}{0,90,180}

\hypersetup{colorlinks=true, urlcolor=accent}
\pagestyle{empty}
\setlength\parindent{0pt}
\setlist[itemize]{leftmargin=*, nosep, topsep=4pt}

\begin{document}

% ==================== HEADER ====================
{\Huge\bfseries\textcolor{heading}{Mehmet Çağrı Ekici}}
\vspace{8pt}

\begin{itemize}[leftmargin=1.5em]
\item \faEnvelope\, \href{mailto:mehmetcagriekici@gmail.com}{mehmetcagriekici@gmail.com}
\item \faPhone\, +90 536 477 17 89
\item \faMapMarker\, Ankara, Turkey
\item \faGithub\, \href{https://github.com/mehmetcagriekici}{github.com/mehmetcagriekici}
\item \faLinkedin\, \href{https://www.linkedin.com/in/mehmetcagriekici}{linkedin.com/in/mehmetcagriekici}
\end{itemize}

\vspace{0.6cm}

% ==================== ABOUT ME ====================
{\LARGE\bfseries\textcolor{heading}{About Me}}\vspace{6pt}
\hrule height 0.8pt
\vspace{6pt}

Backend developer specializing in Go and Python with hands-on experience building distributed systems, AI-powered APIs, and cloud-native applications.

Proficient in pub/sub architecture, RAG pipelines, vector databases, semantic search, and modern backend development practices. Completed Boot.dev's full backend curriculum and actively building production-ready personal projects.

\vspace{0.8cm}

% ==================== SKILLS ====================
{\LARGE\bfseries\textcolor{heading}{Skills}}\vspace{6pt}
\hrule height 0.8pt
\vspace{8pt}

\begin{itemize}
\item Languages: Go, Python, C, JavaScript, TypeScript, SQL
\item Tools \& Technologies: Git, Docker, Kubernetes, RabbitMQ, FastAPI, ChromaDB, Sentence Transformers, CI/CD (GitHub Actions), Linux
\item Databases: PostgreSQL
\end{itemize}

\vspace{0.6cm}

% ==================== PROJECTS ====================
{\LARGE\bfseries\textcolor{heading}{Projects}}\vspace{6pt}
\hrule height 0.8pt
\vspace{6pt}

\textbf{Reargs Similarity API} \hfill \textit{Python, FastAPI, ChromaDB, Sentence Transformers, Gemini LLM}\\[8pt]
Semantic document analysis API that identifies patterns, redundancies, and similarities in writing (supports .txt, .md, .pdf uploads).

\vspace{2pt}
Features file processing, automatic clustering via vector embeddings, persistent storage in Chroma vector database, natural language querying of similar content, LLM-powered content generation from selected clusters, and collection management (create/delete).

\vspace{2pt}
Built with FastAPI, includes automated CI pipeline (GitHub Actions) for testing on every push, and fully Dockerized with multi-stage build for production deployment.

\vspace{4pt}
\faGithub\, \href{https://github.com/mehmetcagriekici/reargs}{github.com/mehmetcagriekici/reargs}\\
\faGlobe\, \href{https://huggingface.co/spaces/mhmtcgrkc/reargs}{Live API Demo}

\vspace{0.6cm}

\textbf{BlightSanest} \hfill \textit{Go, RabbitMQ, Docker, Python, FastAPI, Sentence Transformers, PostgreSQL}\\[8pt]
CLI financial asset analysis tool built on pub/sub architecture with caching and hybrid search.

\vspace{2pt}
Core client/server in Go with RabbitMQ for message distribution; integrated semantic search engine (Python/FastAPI) and persistent storage (PostgreSQL). Fetches third-party financial data, caches results to minimize API calls, supports concurrent analysis algorithms, and enables hybrid (keyword + vector) search over stored assets.

\vspace{4pt}
\faGithub\, \href{https://github.com/mehmetcagriekici/blightsanest}{github.com/mehmetcagriekici/blightsanest}

\vspace{0.6cm}

% ==================== EDUCATION ====================
{\LARGE\bfseries\textcolor{heading}{Education}}\vspace{6pt}
\hrule height 0.8pt
\vspace{6pt}

\textbf{Boot.dev Backend Career Path (Python \& Go)} \hfill 2025 -- Present \\[6pt]
Completed 29 courses and 12 projects covering Go, Python, SQL, distributed systems, HTTP servers/clients, pub/sub (RabbitMQ), Docker, Kubernetes, CI/CD (GitHub Actions), cryptography, and more.

\vspace{4pt}
\href{https://www.boot.dev/u/callsower}{Boot.dev Profile: callsower}

\end{document}
